We thank all 36,982 members of the \sw community for their
contributions to the project so far. A complete list of registered
collaborators is provided at \texttt{http://spacewarps.org/\#/projects/CFHTLS}.
We also thank the anonymous referee for useful comments on the paper.

PJM was given support by the Royal Society, in the form of a research
fellowship, and by the U.S. Department of Energy under contract number DE-AC02-76SF00515.
%
AV acknowledges support from the Leverhulme Trust in the form of a research
fellowship.
%
The work of AM and SM was supported by World Premier International Research
Center Initiative (WPI Initiative), MEXT, Japan. AM acknowledges the support of
the Japan Society for Promotion of Science (JSPS) fellowship. The work of AM
was also supported in part by National Science Foundation Grant No.
PHYS-1066293 and the hospitality of the Aspen Center for Physics. 
%
% Zooniverse / Sloan Foundation.
%
% Other authors.

The \sw project is open source.
The web app was developed at \texttt{https://github.com/Zooniverse/Lens-Zoo}, and was supported by a grant from the Alfred P. Sloan Foundation, 
while the SWAP analysis software was developed at
\texttt{https://github.com/drphilmarshall/SpaceWarps}.

The CFHTLS data used in this work are based on observations obtained with
MegaPrime/MegaCam, a joint project of CFHT and CEA/IRFU, at the
Canada-France-Hawaii Telescope (CFHT) which is operated by the National Research
Council (NRC) of Canada, the Institut National des Science de l'Univers of the
Centre National de la Recherche Scientifique (CNRS) of France, and the
University of Hawaii. This work is based in part on data products produced at
Terapix available at the Canadian Astronomy Data Centre as part of the
Canada-France-Hawaii Telescope Legacy Survey, a collaborative project of NRC and
CNRS.
